Overview

### 2024-08-14 index.qmd
chore(quarto): minor python to ensure site working
docs(quarto): reworked into a book with empty pages to complete

---
authors:
  - name: Amy Heather
    url: https://github.com/amyheather
    orcid: 0000-0002-6596-3479
    affiliation: University of Exeter
---

Summary of the six computational reproducibility assessments conducted as part of STARS Work Package 1. These assessed six discrete-event simulation papers with models in Python and R.

>>>>

---
title: Overview
authors:
  - name: Amy Heather
    url: https://github.com/amyheather
    orcid: 0000-0002-6596-3479
    affiliation: University of Exeter
---

TODO: Overview page
